\mytitle

### 2023-05-25 paper-seb-main.tex
Sorting out git-prep in makefile
Removed git temp files

Paradoxically the science could not mature until there was consensus in scientific methodologies for thermometry, and having a consensus in turn depended on reproducible thermometer measurements; for example, scientists working in different places needed to know they were working with the ``same temperatures'' yet there was for a long period no consensus on what that meant. Contributing to reliable science depended on a thorough understanding of principles, including gradually fixing the confounding factors that were misunderstood \cite{temperature}.\footnote{One example: if the volume of mercury is chosen to measure temperature, a confounding factor is that the volume of the container measuring the mercury volume also increases with temperature (but at a different rate), so the volume measurement is inaccurate.} 
Science matured from no quantitative interest in temperature, through a complex process of hand-in-hand theoretical-and-technical maturation, until today, when we have robust off-the-shelf instruments that measure temperature in reliable, repeatable, internationally standardized units, that follow international quality standards.

@@

\newcount \bibitemn \bibitemn = 0
\newcount \bibnewcolumn

\bibnewcolumn = 122 % bibentry number of last entry on (final) left hand column
% Hint: set it to a very large number, so the final column is as unbalanced as it gets
% then, if it's worth fixing the final page, lower the number to some citation on the 
% lower part of the left hand column; this citation will then become the last in that
% column. Hopefully the righthand column will be of equal length!
% PS Don't forget to check there is nothing on the following page!

>>>>

Paradoxically the science could not mature until there was consensus in scientific methodologies for thermometry, and having that consensus in turn depended on reproducible thermometer measurements; for example, scientists working in different places needed to know they were working with the ``same temperatures'' yet there was for a long period no consensus on what that meant. Contributing to reliable science depended on a thorough understanding of principles, including gradually fixing the confounding factors that were misunderstood \cite{temperature}.\footnote{One example: if the volume of mercury is chosen to measure temperature, a confounding factor is that the volume of the container measuring the mercury volume also increases with temperature (but at a different rate), so the volume measurement is inaccurate.} 
Science matured from no quantitative interest in temperature, through a complex process of hand-in-hand theoretical-and-technical maturation, until today, when we have robust off-the-shelf instruments that measure temperature in reliable, repeatable, internationally standardized units, that follow international quality standards.

@@

\newcount \bibitemn \bibitemn = 0
\newcount \bibnewcolumn 
w
\bibnewcolumn = 122 % bibentry number of last entry on (final) left hand column
% Hint: set it to a very large number, so the final column is as unbalanced as it gets
% then, if it's worth fixing the final page, lower the number to some citation on the 
% lower part of the left hand column; this citation will then become the last in that
% column. Hopefully the righthand column will be of equal length!
% PS Don't forget to check there is nothing on the following page!
